Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-23 LCAforActiveSonarImaging/lca.tex
Adding old files.

\subsection{Oversampling and steering}

Adaptive beamformers process each pixel in a different way in an attempt to surpass the conventional limit of resolution and noise suppression. This non-linear processing of the image increases its bandwidth and introduces a need for oversampling. For MVDR a lateral oversampling factor of up to 10 times is often needed to ensure spatial shift-invariance~\cite{Asen2014}.

Too much steering, beamformer becomes too agressive. Uncertainty in source amplitude grows.

@@

@@

\begin{align*}
d = \frac{\pi\,\theta_\text{open}\,\lambda}{M\,d\,O_s}
\end{align*}

\begin{align}
\w[\beta, \phi] = \text{kaiser}(\beta) = \bmat{
1 \\
e^{-j\frac{md}{\lambda}\sin(\phi)} \\
\vdots\\
e^{-j\frac{(M-1)d}{\lambda}\sin(\phi)}
}
\end{align}

See section \ref{kaiser_windows}.

>>>>

@@

\subsection{Oversampling}

Adaptive beamformers process each pixel in a different way in an attempt to surpass the conventional limit of resolution and noise suppression. This non-linear processing of the image increases its bandwidth and introduces a need for oversampling. For MVDR a lateral oversampling factor of up to 10 times is often needed to ensure spatial shift-invariance in source amplitude~\cite{Asen2014}.

@@

\begin{align}
d = \frac{\pi\,\theta_\text{open}\,\lambda}{M\,d\,O_s}
\end{align}

% See section \ref{kaiser_windows}.
